Dataset analysis with simple regression and Knn models

### 2024-09-06 article/article.tex
add the new file

\title{U1}
\author{Rodriguez González José Adrián }
\date{August 2024}

@@

Some of the related works(by now, I'll just let some of the books and the documentation that I could  to see)

@@

  \begin{tabular}{|m{2.5cm}|m{2.5cm}|m{2.5cm}|m{2.5cm}|m{2.5cm}|}

@@

@@

@@

However it'll be required to know some metrics that will help us to find out how efficient is our model and to know the error that we have in our model too
\begin{itemize}
  \item $R^2$: This metric can measure how much the model can describe the phenom. The $R^2 \in [0,1]$ and if the model tends to 1 the model can describe better the phenom and can be more precise in the predictions.
  \item $MSE$ and $RMSE = $ Are metrics that measure the distance between the value predict against the real value.
  $$MSE=\frac{1}{n}\Sigma^{n}_{i=1}(y_i-\hat{y}_i)^2 $$
    $$RMSE=\sqrt{\frac{1}{n}\Sigma^{n}_{i=1}(y_i-\hat{y}_i)^2} $$
    The difference between MSE and RMSE are that MSE is susceptible to detect outliers values due to the nature of a square function, and also it helps to know the variance that we got in our model. Nevertheless, RMSE use the same scale of the values and want to measure the error as it is on the data.

@@

\subsection{Knn model}
It consist in to look out on the data and predict a value according to the vicinity of the values nearest from the data that is presented. Knn presents two basic hyperparameter, the first one is the number of vicinity and the second is the type of distance that it'll be chosen.
Knn model has some different parameters if we measure it as classifier. However at this case it'll be used the Knn model as a regressor, so it'll be usable the metrics that it has been described before.
(figure \ref{fig:example4})
\begin{figure}[h]
  \centering
\begin{tikzpicture}
  \begin{axis}[
      width=8cm, height=8cm,
      xlabel={$x_1$},
      ylabel={$x_2$},
      grid=major,
      legend pos=outer north east,
      domain=0:5,
      samples=100
  ]
      % Define the coordinates of two classes
      \addplot[only marks, red, mark=o] plot coordinates {(1,1) (1.5,2) (2,1) (2.5,1.5)};
      \addplot[only marks, blue, mark=x] plot coordinates {(3,3) (3.5,3.5) (4,3.2) (4.5,4)};

@@

\section{Data analysis}
\subsection{first dataset}
The first data analysis that has been studied was the dataset with synthetic data. As it had been mentioned, following the scientific methodology we look for the data and it started with a data exploration.
It obtained the following values 
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
   parameter & y & x \\ \hline
   number of values & 506.000000 & 506.000000\\
   mean  &  22.528854  &  3.613524\\
   std   &   9.182176  &  8.601545\\
   minimum   &   5.000000  &  0.006320\\
   percentile $25$   &  17.025000  &  0.082045\\
   percentile $50$   &  21.200000  &  0.256510\\
   percentile $75$   &  25.000000 &   3.677083\\
   maximum   &  50.000000  & 88.976200\\
   \hline
  \end{tabular}
\end{center}
Now that we have assured that the data are completed we can see the value of the mean and the 50 percentile are quite different, mostly on the variable x, it requires to be cleaned the data. Nevertheless, it is useful to check the correlation with variable x to y too.
The correlation matrix resulted on 
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
      & y & x  \\ \hline
     y&  1.000000 & -0.389582 \\
     x & -0.389582  & 1.000000 \\
     \hline
  \end{tabular}
\end{center}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.35\textwidth]{data1_plot1.png}
  \caption{E}
  \label{fig:ejemplo}
\end{figure}

The correlation is quite low between x,y. That means that it'll be hard to find a relation with the x and y with linear regression.
And also, something that we can notice with the plots that they are not normally distributed. The x-axis it seems more a exponential distribution than normal.
Other way to demonstrate it could making a hypothesis test and verifying it with a Shapiro-walk; it consist to propose a null hypothesis, that if the value of statistic is closer to 1 or great, it will reject the hypothesis, therefore the distribution doesn't follow a normal distribution. By other hand if we encounter a value smaller it will indicate is that probably the distribution follows a normal distribution. And also we have de p value that if is greater than 0.05 will indicate that is a normal distribution, in the opposite way it is a non-normal distribution.
The test concluded with a distribution of  $4.85*10^-28$ so it is not a normal distribution.
At this point we can choose several ways to follow
\begin{itemize}
  \item Trying to normalizing
  \item Trying with models more associated with exponential distributions or models that will no depend on the distribution.
  \item Infer with other features
\end{itemize} 
Due to the objectives of the work, the first attempt it'll be used.
At this dataset has been followed 4 approaches to look the efficiency of methods at the cleaning of the data.
However, it has been tested several types of transformations to check out if it'll be more useful the logarithm transformation according with the parameter of skew

\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
     type-skew & x & y  \\ \hline
     original& 5.223148798243851&1.1109118502479587\\
     log&1.2692005882725572&-0.24563979611568673\\
     sqrt&2.024382103123676&0.4381663127860419\\
     1/x&-0.5772191040682719&1.9393215717506038\\
     box-cox&0.093649&\dots\\
     outliers&0.40335&1.058543\\
      \hline
  \end{tabular}
\end{center}
It could seems some techniques are better however logarithm transformation has a better resolution in the skew of both variables.    
\subsection{first method}
The first approach to make a model was transforming with logarithm and making a cross validation
\begin{figure}[h]
  \centering
  \includegraphics[width=0.35\textwidth]{model_1.png}
  \caption{Lineal regression}
  \label{fig:example_1}
\end{figure}
And therefore it was contrasted with the Knn model, getting the next values

\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
     metric & Lineal regression & Knn \\ \hline
     $R^2$l& 35.488840060699256\%&43.57\\
     MSE&0.09611374428381783&0.11904\\
     RMSE&0.30971201639466434&0.33166\\
     \hline
    %
  \end{tabular}
\end{center}
The model has been contrasted with both models and with the same cleaned data, as also trained at the same way respectively at the model 
However, the Lineal regressor has been predicting the data within the confidence.
For example, it added a value x on 2.3 and the result in y is 2.7534 
The confidence value on 95\% interval is  from $(2.172214750599946, 3.334689169873629)$
and is has been seen the value was fitted correctly.
\begin{figure}[h]
  \includegraphics[width=0.35\textwidth]{data2_plot.png}
  \caption{Lineal regression with the intervals set}

  \label{fig:example_intervals}
\end{figure}
However it has been made a generalized model to linear regression in a set of dots (fig\ref{fig:example_intervals})
The equation for this model is 
$$y=-0.21773690693332431x+3.2542468461834333$$
\subsection{Second method}
The second approach it consisted to just transforming the value with logarithm without CV 5x2
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
     metric & Lineal regression & Knn \\ \hline
     $R^2$& 15.0589474050694\%&22.562569548739275\%\\
     MSE&0.1127456496305317&0.11904364904719832\\
     RMSE&0.3357761897909554&0.33166\\
     \hline
  \end{tabular}
\end{center}
The values obtained are quite low, and the test of interval values with a random value it has been displayed 
\begin{figure}[h]
  \includegraphics[width=0.35\textwidth]{model_2.png}
  \caption{Lineal regression with the confidence intervals}

  \label{fig:example_intervals}
\end{figure}
The random value tested was $x=2.3$ $ y=2.712267315$
The CI of  95\% for 2.3 $(2.1310301053631586, 3.2935045246368415)$
so the equation resulting is: $$y=3.28236728 -0.24786955x $$

\subsection{third method}
The outliers were fixed with capping and flooring methods using the median
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
     metric & Lineal regression & Knn \\ \hline
     $R^2$& 32.19327627743514\%&32.92025378085354\%\\
     MSE& 0.002590185931743603&0.09954163106601016\\
     RMSE&0.3097120163946644&0.3155021886\\
     \hline

  \end{tabular}
\end{center}
\begin{figure}[h]
  \includegraphics[width=0.35\textwidth]{model_3_3.png}
  \caption{Lineal regression with the confidence intervals}

@@

\subsection{fourth method}
The last methods were used at this model. And also the test of Knn, was a little bit different to due it has been included the type of distance
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
     metric & Lineal regression & Knn \\ \hline
     $R^2$& 37.1 \%&38.88337562736399\%\\
     MSE& 0.08067515724063212&0.06685108607726611\\
     RMSE&0.2839075215367599&0.3155021886\\
     \hline

  \end{tabular}
\end{center}
Although, for this search of parameters, it got the Minkowski dataset, and finally the value of the intervals and equation are described as 
The random value tested was $x=0.4$ $ y=3.1646101221355143$
The CI of  95\% for 2.3 $(2.624302151585808, 3.7049180926852205)$
so the equation resulting is: $$y=3.2466778431246275 -0.20516930247278303x $$

@@

And one of the most important things that it has obtained is this table that compiles all the metrics and parameters that has been obtaining
\begin{table}[h]
  \scriptsize 
  \setlength{\extrarowheight}{-2pt} 
  \begin{tabular}{|l|l|l|}
  \hline
  \textbf{Metric} & \textbf{model1} & \textbf{model2} \\
  \hline
  $R^2$ & 35.4\% & 15.05\% \\
  \hline
  MSE & 0.0961 & 0.1127 \\
  \hline
  RMSE & 0.3097 & 0.3358 \\
  \hline
  EQUATION & $y=-0.2177x+3.2542$ & $y=-0.2479x+3.2824$ \\
  \hline
  Adjusted $R^2$ & 36.7\% & 39.8\% \\
  \hline
  F-statistic & 147.1 & 267.1 \\
  \hline
  $P(F-statistic)$ & 5.97e-27 & 2.11e-46 \\
  \hline
  Log-Likelihood & -50.079 & -91.384 \\
  \hline
  AIC & 104.2 & 186.8 \\
  \hline
  BIC & 111.2 & 194.8 \\
  \hline
  std error & const=0.024, x=0.018 & const=0.019, x=0.015 \\
  \hline
  $\sigma$ & const=135.161, x=-12.128 & const=170.036, x=-16.343 \\
  \hline
  $P>\|t\|$ & const: 0.000, x: 0.000 & const: 0.000, x: 0.000 \\
  \hline
  Confidence Intervals & const=[3.2068, 3.3017], x=[-0.2531, -0.1824] & const=[3.2444, 3.3203], x=[-0.2777, -0.2181] \\
  \hline
  Omnibus & 41.738 & 37.308 \\
  \hline
  Prob(Omnibus) & 0.000 & 0.000 \\
  \hline
  Jarque-Bera (JB) & 64.331 & 64.192 \\
  \hline
  Prob(JB) & 1.07e-14 & 1.15e-14 \\
  \hline
  Skew & 0.960 & 0.581 \\
  \hline
  Kurtosis & 4.553 & 4.570 \\
  \hline
  Durbin-Watson & 0.983 & 1.902 \\
  \hline
  Condition Number & 2.26 & 2.16 \\
  \hline
  \end{tabular}
  \caption{Model comparison 1 and 2}
  \label{tab:modelos12}
  \end{table}
  \begin{table}[H]

  \scriptsize 
    \setlength{\extrarowheight}{-2pt}

  \begin{tabular}{|l|l|l|}
  \hline
  \textbf{Metric} & \textbf{model3} & \textbf{model4} \\
  \hline
  $R^2$ & 32.193\% & 37.1\% \\
  \hline
  MSE & 0.014957 & 0.0807 \\
  \hline
  RMSE & 0.12224 & 0.2839 \\
  \hline
  EQUATION & $y=-0.30537x+1.85673$ & $y=-0.2052x+3.2467$ \\
  \hline
  Adjusted $R^2$ & 33.5\% & 36.8\% \\
  \hline
  F-statistic & 128.2 & 147.8 \\
  \hline
  $P(F-statistic)$ & 2.76e-24 & 4.72e-27 \\
  \hline
  Log-Likelihood & 181.27 & -32.091 \\
  \hline
  AIC & -385.5 & 68.18 \\
  \hline
  BIC & -351.5 & 75.25 \\
  \hline
  std error & const=1.8567, x=-0.3054 & const=0.022, x=0.017 \\
  \hline
  $\sigma$ & const=0.015, x=0.027 & const=144.464, x=-12.159 \\
  \hline
  $P>\|t\|$ & const: 0.000, x: 0.000 & const: 0.000, x: 0.000 \\
  \hline
  Confidence Intervals & const=[1.8279, 1.886], x=[-0.3584, -0.2522] & const=[3.2024, 3.2909], x=[-0.2384, -0.1719] \\
  \hline
  Omnibus & 40.637 & 35.555 \\
  \hline
  Prob(Omnibus) & 0.000 & 0.000 \\
  \hline
  Jarque-Bera (JB) & 56.377 & 46.953 \\
  \hline
  Prob(JB) & 5.73e-13 & 6.37e-11 \\
  \hline
  Skew & 1.021 & 0.938 \\
  \hline
  Kurtosis & 4.087 & 3.966 \\
  \hline
  Durbin-Watson & 0.966 & 0.958 \\
  \hline
  Condition Number & 4.45 & 2.26 \\
  \hline
  \end{tabular}
  \caption{Model comparison 3 and 4}
  \label{tab:modelos34}
  \end{table}

\subsection{Second dataset}
The next dataset that it has been studying was about cars. It is a car's magazine from 1985 that compiles prices and features from several cars. 
For this dataset it has been read some papers(include the cite) to understand some of the features and its relationship. 
As a one of the first steps was the cleaning the data, and a data exploration was made to look for missing values and 
\begin{center}
\begin{figure}[H]
  \includegraphics[width=1\textwidth]{heatmap.png}
  \caption{The heatmap of correlation}
  \label{fig:heatmap}
\end{figure}
\end{center}
The heatmap (Figure \ref{fig:heatmap}) represents how is related a variable with other. As the objective of the study is to making a model that can predict the price of cars according to certain variables. 
However a tool that can save time it is to see the correlation with continuous variables. So those variables that have been analyzed were the Curb weight, engine size, horsepower city-mpg and highway-mpg.
The procedure to clean up the data was the same as the previous dataset however some columns contained a few NaN values and they must be changed. As also, some features are measured by different magnitudes, for example, amounts of money and horse power, so it would useful to standardize the data and also it could be applied a logarithm transformation due to some the dataset wasn't following a normal distribution, instead it was a exponential distribution(figure \ref{fig:box},\ref{fig:box2}).
\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{box.png}
      \caption*{Example when the data is not standardized}
      \label{fig:box}
  \end{minipage}
  \begin{minipage}[b]{0.3\textwidth}
      \centering
      \includegraphics[width=\textwidth]{box2.png}
      \caption*{Example when data uis standardized and transformed}
      \label{fig:box2}
  \end{minipage}
\end{figure}
\subsection{Engine size}
\begin{tabular}{|c|c|c|}
  \hline
   metric & Lineal regression & Knn \\ \hline
   $R^2$& 73.62087367142167 \%&78.14960577066459\%\\
   MSE& 0.00992703573774292&0.008260694761950247\\
   RMSE&0.09960553714701531&0.09078358735816178\\
   \hline

Prediction for x=0.9: 0.873558685297521
Ci of  95\%for x=0.9: (0.6755512178129525, 1.0715661527820897)
$$y=1.0421234211972827x-0.06435239378003343$$
\subsection{Miles per gallon on city }
\begin{tabular}{|c|c|c|}
  \hline
   metric & Lineal regression & Knn \\ \hline
   $R^2$& 60.45640689950125 \%&63.98078808830601\%\\
   MSE&0.020279279592056144&0.01864935309235264\\
   RMSE&0.14237431771458053&0.13622653661454523\\
   \hline

Prediction for x=0.9: 0.001530863668857796
Ci of 95\%for x=0.9: (-0.2679841644933157, 0.2710458918310313)
$$y=-0.847735376275263x+0.7644927023165945$$
%%
\subsection{Highway miles per gallon }
\begin{tabular}{|c|c|c|}
  \hline
   metric & Lineal regression & Knn \\ \hline
   $R^2$& 60.26238063837296 \%&71.4051650378093\%\\
   MSE&0.020296748345956392&0.01473467535564263\\
   RMSE&0.14246665691899474&0.12126069885616314\\
   \hline

Prediction for x=0.9: 0.029920806311725112
Ci of  95\%for x=0.9: (-0.23756924465403179, 0.297410857277482)
$$y=-0.8749508264218194x+0.8173765500913626$$
%%
\subsection{Curb weight}
\begin{tabular}{|c|c|c|}
  \hline
   metric & Lineal regression & Knn \\ \hline
   $R^2$& 75.95183149109518 \%&75.37829642479748\%\\
   MSE&  0.012140499045124736& 0.012413594738192302\\
   RMSE&0.1262230883265539&0.11115941370057997\\
   \hline
\end{tabular}

Prediction for x=0.9: 0.8331700416235279
Ci of  95\%for x=0.9: (0.6006405680156519, 1.065699515231404)
$$y=0.9548221722260348x -0.026169913379903483$$

\subsection{Horse power}
\begin{tabular}{|c|c|c|}
  \hline
   metric & Lineal regression & Knn \\ \hline
   $R^2$& R²: 69.07940114232951 \%&43.319290242601016\%\\
   MSE&  0.08221699892102004& 0.13686099980559793\\
   RMSE&0.28673506747696564&0.3696553507791872\\
   \hline
\end{tabular}

>>>>

\title{Dataset analysis with simple regression and Knn models}
\author{Rodriguez González José Adrián }
\date{August 2024}

@@

Articles that were helpful to compare results and methodologies.
\begin{table}[H]

@@

  \begin{tabular}{|m{2.5cm}|m{2.5cm}|m{2.5cm}|m{2.5cm}|m{2.9cm}|}

@@

  \caption{Literature related with the work}

@@

\end{table}

@@

However it'll be required to know some metrics that will help us to find out how efficient is our model and to know the error that we have in our model too\citep{bruce2020practical}
\begin{itemize}
  \item $R^2$: This metric can measure how much the model can describe the phenom. The $R^2 \in [0,1]$ and if the model tends to 1 the model can describe better the phenom and can be more precise in the predictions.
  \item $MSE$ and $RMSE = $ Are metrics that measure the distance between the value predict against the real value.
  $$MSE=\frac{1}{n}\Sigma^{n}_{i=1}(y_i-\hat{y}_i)^2 $$
    $$RMSE=\sqrt{\frac{1}{n}\Sigma^{n}_{i=1}(y_i-\hat{y}_i)^2} $$
    The difference between MSE and RMSE are that MSE is susceptible to detect outliers values due to the nature of a square function, and also it helps to know the variance that we got in our model. Nevertheless, RMSE use the same scale of the values and want to measure the error as it is on the data.

@@

\subsection{Knn model}
It consist in to look out on the data and predict a value according to the vicinity of the values nearest from the data that is presented. Knn presents two basic hyperparameter, the first one is the number of vicinity and the second is the type of distance that it'll be chosen.
Knn model has some different parameters if we measure it as classifier. However at this case it'll be used the Knn model as a regressor, so it'll be usable the metrics that it has been described before.
(figure \ref{fig:example4})
\begin{figure}[H]
  \centering
\begin{tikzpicture}
  \begin{axis}[
      width=8cm, height=8cm,
      xlabel={$x_1$},
      ylabel={$x_2$},
      grid=major,
      legend pos=outer north east,
      domain=0:5,
      samples=100
  ]
      % Define the coordinates of two classes
      \addplot[only marks, red, mark=o] plot coordinates {(1,1) (1.5,2) (2,1) (2.5,1.5)};
      \addplot[only marks, blue, mark=x] plot coordinates {(3,3) (3.5,3.5) (4,3.2) (4.5,4)};

@@

\section{Data analysis}
\subsection{first dataset}
The first data analysis that has been studied was the dataset with synthetic data. As it had been mentioned, following the scientific methodology we look for the data and it started with a data exploration.
It obtained the following values 
\begin{table}[H]
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
   parameter & y & x \\ \hline
   number of values & 506.000000 & 506.000000\\
   mean  &  22.528854  &  3.613524\\
   std   &   9.182176  &  8.601545\\
   minimum   &   5.000000  &  0.006320\\
   percentile $25$   &  17.025000  &  0.082045\\
   percentile $50$   &  21.200000  &  0.256510\\
   percentile $75$   &  25.000000 &   3.677083\\
   maximum   &  50.000000  & 88.976200\\
   \hline
  \end{tabular}
  \caption{Parameters}
\end{center}
\end{table}
Now that we have assured that the data are completed we can see the value of the mean and the 50 percentile are quite different, mostly on the variable x, it requires to be cleaned the data. Nevertheless, it is useful to check the correlation with variable x to y too.
The correlation matrix resulted on 
\begin{table}[H]
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
      & y & x  \\ \hline
     y&  1.000000 & -0.389582 \\
     x & -0.389582  & 1.000000 \\
     \hline
  \end{tabular}
  \caption{Correlation}
\end{center}
\end{table}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.65\textwidth]{data1_plot1.png}
  \caption{Exploratory data}
  \label{fig:ejemplo}
\end{figure}

The correlation is quite low between x,y. That means that it'll be hard to find a relation with the x and y with linear regression.
And also, something that we can notice with the plots that they are not normally distributed. The x-axis it seems more a exponential distribution than normal.
Other way to demonstrate it could making a hypothesis test and verifying it with a Shapiro-walk; it consist to propose a null hypothesis, that if the value of statistic is closer to 1 or great, it will reject the hypothesis, therefore the distribution doesn't follow a normal distribution. By other hand if we encounter a value smaller it will indicate is that probably the distribution follows a normal distribution. And also we have de p value that if is greater than 0.05 will indicate that is a normal distribution, in the opposite way it is a non-normal distribution.
The test concluded with a distribution of  $4.85*10^-28$ so it is not a normal distribution.
At this point we can choose several ways to follow
\begin{itemize}
  \item Trying to normalizing
  \item Trying with models more associated with exponential distributions or models that will no depend on the distribution.
  \item Infer with other features
\end{itemize} 
Due to the objectives of the work, the first attempt it'll be used.
At this dataset has been followed 4 approaches to look the efficiency of methods at the cleaning of the data.
However, it has been tested several types of transformations to check out if it'll be more useful the logarithm transformation according with the parameter of skew 
\begin{table}[H]
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
     type-skew & x & y  \\ \hline
     original& 5.223148798243851&1.1109118502479587\\
     log&1.2692005882725572&-0.24563979611568673\\
     sqrt&2.024382103123676&0.4381663127860419\\
     1/x&-0.5772191040682719&1.9393215717506038\\
     box-cox&0.093649&\dots\\
     outliers&0.40335&1.058543\\
      \hline
  \end{tabular}
\end{center}
\caption{Skewness in different types of transformations}
\end{table}
It could seems some techniques are better however logarithm transformation has a better resolution in the skew of both variables.    
\subsection{First method}
The first approach to make a model was transforming with logarithm and making a cross validation
\begin{figure}[h]
  \centering
  \includegraphics[width=0.65\textwidth]{model_1.png}
  \caption{Lineal regression}
  \label{fig:example_1}
\end{figure}
And therefore it was contrasted with the Knn model, getting the next values
\begin{table}[H]
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
     metric & Lineal regression & Knn \\ \hline
     $R^2$l& 35.488840060699256\%&43.57\\
     MSE&0.09611374428381783&0.11904\\
     RMSE&0.30971201639466434&0.33166\\
     \hline
    %
  \end{tabular}
  \caption{First table}
\end{center}
\end{table}
The model has been contrasted with both models and with the same cleaned data, as also trained at the same way respectively at the model 
However, the Lineal regressor has been predicting the data within the confidence.
For example, it added a value x on 2.3 and the result in y is 2.7534 
The confidence value on 95\% interval is  from $(2.172214750599946, 3.334689169873629)$
and it has been seen the value was fitted correctly.
The best parameters found on kNN was with 21 neighbors and manhattan distance
\begin{figure}[h]
  \center
  \includegraphics[width=0.65\textwidth]{data2_plot.png}
  \caption{Lineal regression with the intervals set}

  \label{fig:example_intervals}
\end{figure}
However it has been made a generalized model to linear regression in a set of dots (fig\ref{fig:example_intervals})
The equation for this model is 
$$y=-0.21773690693332431x+3.2542468461834333$$
\subsection{Second method}
The second approach it consisted to just transforming the value with logarithm without CV 5x2
\begin{table}[H]
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
     metric & Lineal regression & Knn \\ \hline
     $R^2$& 15.0589474050694\%&43.57674995779635\%\\
     MSE&0.1127456496305317&0.11904364904719832\\
     RMSE&0.3357761897909554&0.33166\\
     \hline
  \end{tabular}
  \caption{Second model}
\end{center}
\end{table}
The values obtained are quite low, and the test of interval values with a random value it has been displayed 
\begin{center}

\begin{figure}[h]
  \center
  \includegraphics[width=0.65\textwidth]{model_2.png}
  \caption{Lineal regression with the confidence intervals}
  \label{fig:example_intervals}
\end{figure}
\end{center}
The random value tested was $x=2.3$ $ y=2.712267315$
The CI of  95\% for 2.3 $(2.1310301053631586, 3.2935045246368415)$
so the equation resulting is: $$y=3.28236728 -0.24786955x $$

Here it found with 21 neighbors but with cosine distance
\subsection{Third method}
The outliers were fixed with capping and flooring methods using the median
\begin{table}[H]
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
     metric & Lineal regression & Knn \\ \hline
     $R^2$& 32.19327627743514\%&32.92025378085354\%\\
     MSE& 0.002590185931743603&0.09954163106601016\\
     RMSE&0.3097120163946644&0.3155021886\\
     \hline

  \end{tabular}
  \caption{Third method}

\end{center}
\end{table}
\begin{figure}[h]
  \center
  \includegraphics[width=0.65\textwidth]{model_3_3.png}
  \caption{Lineal regression with the confidence intervals}

@@

\subsection{fourth method}
The last methods were used at this model. And also the test of Knn, was a little bit different to due it has been included the type of distance
\begin{table}[H]
\begin{center}
  \begin{tabular}{|c|c|c|}
    \hline
     metric & Lineal regression & Knn \\ \hline
     $R^2$& 37.1 \%&38.88337562736399\%\\
     MSE& 0.08067515724063212&0.06685108607726611\\
     RMSE&0.2839075215367599&0.3155021886\\
     \hline

  \end{tabular}
\end{center}
\caption{The four method}
\end{table}
Although, for this search of parameters, it got the Minkowski dataset, and finally the value of the intervals and equation are described as 
The random value tested was $x=0.4$ $ y=3.1646101221355143$
The CI of  95\% for 2.3 $(2.624302151585808, 3.7049180926852205)$
so the equation resulting is: $$y=3.2466778431246275 -0.20516930247278303x $$

@@

And one of the most important things that it has obtained is this table that compiles all the metrics and parameters that has been obtaining
\begin{table}[h]
  \small 
  \setlength{\extrarowheight}{-2pt} 
  \begin{tabular}{|l|l|l|}
  \hline
  \textbf{Metric} & \textbf{model1} & \textbf{model2} \\
  \hline
  $R^2$ & 35.4\% & 15.05\% \\
  \hline
  MSE & 0.0961 & 0.1127 \\
  \hline
  RMSE & 0.3097 & 0.3358 \\
  \hline
  EQUATION & $y=-0.2177x+3.2542$ & $y=-0.2479x+3.2824$ \\
  \hline
  Adjusted $R^2$ & 36.7\% & 39.8\% \\
  \hline
  F-statistic & 147.1 & 267.1 \\
  \hline
  $P(F-statistic)$ & 5.97e-27 & 2.11e-46 \\
  \hline
  Log-Likelihood & -50.079 & -91.384 \\
  \hline
  AIC & 104.2 & 186.8 \\
  \hline
  BIC & 111.2 & 194.8 \\
  \hline
  std error & const=0.024, x=0.018 & const=0.019, x=0.015 \\
  \hline
  $\sigma$ & const=135.161, x=-12.128 & const=170.036, x=-16.343 \\
  \hline
  $P>\|t\|$ & const: 0.000, x: 0.000 & const: 0.000, x: 0.000 \\
  \hline
  Confidence Intervals & const=[3.2068, 3.3017]  & const=[3.2444, 3.3203] \\
  & x=[-0.2531, -0.1824] &x=[-0.2777, -0.2181]\\
  \hline
  Omnibus & 41.738 & 37.308 \\
  \hline
  Prob(Omnibus) & 0.000 & 0.000 \\
  \hline
  Jarque-Bera (JB) & 64.331 & 64.192 \\
  \hline
  Prob(JB) & 1.07e-14 & 1.15e-14 \\
  \hline
  Skew & 0.960 & 0.581 \\
  \hline
  Kurtosis & 4.553 & 4.570 \\
  \hline
  Durbin-Watson & 0.983 & 1.902 \\
  \hline
  Condition Number & 2.26 & 2.16 \\
  \hline
  \end{tabular}
  \caption{Model comparison 1 and 2}
  \label{tab:modelos12}
  \end{table}
  \begin{table}[H]

  \small
    \setlength{\extrarowheight}{-2pt}

  \begin{tabular}{|l|l|l|}
  \hline
  \textbf{Metric} & \textbf{model3} & \textbf{model4} \\
  \hline
  $R^2$ & 32.193\% & 37.1\% \\
  \hline
  MSE & 0.014957 & 0.0807 \\
  \hline
  RMSE & 0.12224 & 0.2839 \\
  \hline
  EQUATION & $y=-0.30537x+1.85673$ & $y=-0.2052x+3.2467$ \\
  \hline
  Adjusted $R^2$ & 33.5\% & 36.8\% \\
  \hline
  F-statistic & 128.2 & 147.8 \\
  \hline
  $P(F-statistic)$ & 2.76e-24 & 4.72e-27 \\
  \hline
  Log-Likelihood & 181.27 & -32.091 \\
  \hline
  AIC & -385.5 & 68.18 \\
  \hline
  BIC & -351.5 & 75.25 \\
  \hline
  std error & const=1.8567, x=-0.3054 & const=0.022, x=0.017 \\
  \hline
  $\sigma$ & const=0.015, x=0.027 & const=144.464, x=-12.159 \\
  \hline
  $P>\|t\|$ & const: 0.000, x: 0.000 & const: 0.000, x: 0.000 \\
  \hline
  Confidence Intervals & const=[1.8279, 1.886] & const=[3.2024, 3.2909],  \\
  &  x=[-0.3584, -0.2522]&x=[-0.2384, -0.1719]\\
  \hline
  Omnibus & 40.637 & 35.555 \\
  \hline
  Prob(Omnibus) & 0.000 & 0.000 \\
  \hline
  Jarque-Bera (JB) & 56.377 & 46.953 \\
  \hline
  Prob(JB) & 5.73e-13 & 6.37e-11 \\
  \hline
  Skew & 1.021 & 0.938 \\
  \hline
  Kurtosis & 4.087 & 3.966 \\
  \hline
  Durbin-Watson & 0.966 & 0.958 \\
  \hline
  Condition Number & 4.45 & 2.26 \\
  \hline
  \end{tabular}
  \caption{Model comparison 3 and 4}
  \label{tab:modelos34}
  \end{table}

\subsection{Second dataset}
The next dataset that it has been studying was about cars. It is a car's magazine from 1985 that compiles prices and features from several cars. 
For this dataset it has been read some papers(include the cite) to understand some of the features and its relationship. 
As a one of the first steps was the cleaning the data, and a data exploration was made to look for missing values and 
\begin{center}
\begin{figure}[H]
  \center
  \includegraphics[width=1.1\textwidth]{heatmap.png}
  \caption{The heatmap of correlation}
  \label{fig:heatmap}
\end{figure}
\end{center}
The heatmap (Figure \ref{fig:heatmap}) represents how is related a variable with other. As the objective of the study is to making a model that can predict the price of cars according to certain variables. 
However a tool that can save time it is to see the correlation with continuous variables. So those variables that have been analyzed were the Curb weight, engine size, horsepower city-mpg and highway-mpg.
The procedure to clean up the data was the same as the previous dataset however some columns contained a few NaN values and they must be changed. As also, some features are measured by different magnitudes, for example, amounts of money and horse power, so it would useful to standardize the data and also it could be applied a logarithm transformation due to some the dataset wasn't following a normal distribution, instead it was a exponential distribution(figure \ref{fig:box},\ref{fig:box2}).
\begin{figure}[H]
  \centering
  \begin{minipage}[b]{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{box.png}
      \caption*{Example when the data is not standardized}
      \label{fig:box}
  \end{minipage}
  \begin{minipage}[b]{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{box2.png}
      \caption*{Example when data is standardized and transformed}
      \label{fig:box2}
  \end{minipage}
\end{figure}
\subsection{Engine size}
\begin{table}[H]
\begin{tabular}{|c|c|c|}
  \hline
   metric & Lineal regression & Knn \\ \hline
   $R^2$& 73.62087367142167 \%&78.14960577066459\%\\
   MSE& 0.00992703573774292&0.008260694761950247\\
   RMSE&0.09960553714701531&0.09078358735816178\\
   \hline
  \end{tabular}
  \caption{Engine size}
\end{table}
Prediction for x=0.9: 0.873558685297521

Ci of  95\%for x=0.9: (0.6755512178129525, 1.0715661527820897)
$$y=1.0421234211972827x-0.06435239378003343$$
The best parameters obtained were with Minkowski distance with 10 neighbors,  value of $p=1$ and the weight was according with the distance 
\subsection{Miles per gallon on city }
\begin{table}[H]
\begin{tabular}{|c|c|c|}
  \hline
   metric & Lineal regression & Knn \\ \hline
   $R^2$& 60.45640689950125 \%&63.98078808830601\%\\
   MSE&0.020279279592056144&0.01864935309235264\\
   RMSE&0.14237431771458053&0.13622653661454523\\
   \hline
  \end{tabular}
  \caption{ Miles per gallon on city}
\end{table}
Prediction for x=0.9: 0.001530863668857796

Ci of 95\%for x=0.9: (-0.2679841644933157, 0.2710458918310313)
$$y=-0.847735376275263x+0.7644927023165945$$
%%
The best parameters obtained were with Minkowski distance with 10 neighbors,  value of $p=1$ and the weight was uniform
\subsection{Highway miles per gallon }
\begin{table}[H]
\begin{tabular}{|c|c|c|}
  \hline
   metric & Lineal regression & Knn \\ \hline
   $R^2$& 60.26238063837296 \%&71.4051650378093\%\\
   MSE&0.020296748345956392&0.01473467535564263\\
   RMSE&0.14246665691899474&0.12126069885616314\\
   \hline
  \end{tabular}
  \caption{ Highway miles per gallon}
\end{table}
Prediction for x=0.9: 0.029920806311725112
